# Results Psychometric Analyses per Scale


## Communication

### CFA
```{r CFA Communicating, echo=F}
Model_Com<-'
Communicatie=~K_Comm01+
K_Comm02+
K_Comm03+
K_Comm04+
K_Comm05+
K_Comm06+
K_Comm07
'

Fit_Com_G <- cfa(model = Model_Com, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Com_G)
```

### Measurement invariance across Gender
```{r MI communicating gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Com, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI communicating institutions, echo = F, warning = FALSE}


```
MODEL did not converge ... still have to check this out

### Reliability
```{r Communicating, echo = F}
Com_items <- dplyr::select(Goleweb_KYSS, K_Comm01, K_Comm02, K_Comm03, K_Comm04, K_Comm05, K_Comm06, K_Comm07)
Rel_Com <- psych::alpha(Com_items)

colformat_double(flextable(Rel_Com$total), digits = 2)
```


## Diversity

### CFA
```{r CFA Diversity, echo=F}
Model_Div<-'
Diversiteit=~K_Divers01+
K_Divers02+
K_Divers03+
K_Divers04+
K_Divers05+
K_Divers06
'
Fit_Div_G <- cfa(model = Model_Div, data = Goleweb_KYSS, estimator="MLM")
# summary(Fit_Div_G, fit.measures = TRUE, standardized=TRUE)

sem_fitmeasures(Fit_Div_G)

```
Fit measures demonstrate inadequate model fit. Modification indices pointed out that allowing covariance between items K_Divers02 and K_Divers04 would improve model fit.

```{r CFA Diversity 2, echo=F}
Model_Div_2<-'
Diversiteit=~K_Divers01+
K_Divers02+
K_Divers03+
K_Divers04+
K_Divers05+
K_Divers06
K_Divers02 ~~ K_Divers04'

Fit_Div_G2 <- cfa(model = Model_Div_2, data = Goleweb_KYSS, estimator="MLM")

sem_fitmeasures(Fit_Div_G2)

```
Fit measures demonstrate that allowing covariance resulted in adequate model-fit. Analyses also pointed that the second model is significantly better than the first.

```{r CFA Diversity 3, echo=F}

compare_div <- anova (Fit_Div_G, Fit_Div_G2)

flextable(compare_div)

```

### Measurement invariance across Gender
```{r MI diversity gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Div_2, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI diversity institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Div_2, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability

```{r rel Diversity, echo = F}
Div_items_G <- dplyr::select(Goleweb_KYSS, K_Divers01, K_Divers02, K_Divers03, K_Divers04, K_Divers05, K_Divers06)
  rel_div <- psych::alpha(Div_items_G) 
  
  
colformat_double(flextable(rel_div$total), digits = 2)
```


## Cooperation

### CFA
```{r CFA Cooperating, echo=F}
Model_Sam<-'
Samenwerken=~K_Samen01+
K_Samen02+
K_Samen03+
K_Samen04+
K_Samen05+
K_Samen06
'

Fit_Sam_G <- cfa(model = Model_Sam, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Sam_G)
```

### Measurement invariance across Gender
```{r MI cooperating gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Sam, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI cooperating institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Sam, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r cooperation, echo = F}
Sam_items_G <- dplyr::select(Goleweb_KYSS, K_Samen01, K_Samen02, K_Samen03, K_Samen04, K_Samen05, K_Samen06)
Rel_Sam <- psych::alpha(Sam_items_G)

colformat_double(flextable(Rel_Sam$total), digits = 2)
```


## Empathy

### CFA
```{r CFA Empathy, echo=F}
Model_Inl<-'
Inleving=~K_Inlev01+
K_Inlev02+
K_Inlev03+
K_Inlev04+
K_Inlev05+
K_Inlev06
'

Fit_Inl_G <- cfa(model = Model_Inl, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Inl_G)
```

### Measurement invariance across Gender
```{r MI empathy gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Inl, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI empathy institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Inl, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r reliability empathy, echo = F}
Inl_items_G <- dplyr::select(Goleweb_KYSS, K_Inlev01, K_Inlev02, K_Inlev03, K_Inlev04, K_Inlev05, K_Inlev06)
Rel_Inl <- psych::alpha(Inl_items_G)

colformat_double(flextable(Rel_Inl$total), digits = 2)
```


## Result oriented working

### CFA
```{r CFA Result oriented working, echo=F}
Model_Res<-'
Resultaatgerichtheid=~K_Result01+
K_Result02+
K_Result03+
K_Result04+
K_Result05+
K_Result06+
K_Result07
'

Fit_Res_G <- cfa(model = Model_Res, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Res_G)
```

### Measurement invariance across Gender
```{r MI result gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Res, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI result institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Res, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r reliability result oriented, echo = F}
Res_items_G <- dplyr::select(Goleweb_KYSS, K_Result01, K_Result02, K_Result03, K_Result04, K_Result05, K_Result06, K_Result07)
Rel_Res <- psych::alpha(Res_items_G)

colformat_double(flextable(Rel_Res$total), digits = 2)
```


## Digital Skills

### CFA
```{r CFA Digital skills, echo=F}
Model_Dig<-'
Digitale=~K_DigVa01+
K_DigVa02+
K_DigVa03+
K_DigVa04
'

Fit_Dig_G <- cfa(model = Model_Dig, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Dig_G)
```

### Measurement invariance across Gender
```{r MI digital gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Dig, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI digital institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Dig, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r reliability digital, echo = F}
Digit_items_G <- dplyr::select(Goleweb_KYSS, K_DigVa01, K_DigVa02, K_DigVa03, K_DigVa04)
Rel_Digit <- psych::alpha(Digit_items_G)

colformat_double(flextable(Rel_Digit$total), digits = 2)
```


## Flexibility

### CFA
```{r CFA Flexibility, echo=F}
Model_Fle<-'
Flexibiliteit=~K_Flex01+
K_Flex02+
K_Flex03+
K_Flex04+
K_Flex05+
K_Flex06
'
Fit_Fle_G <- cfa(model = Model_Fle, data = Goleweb_KYSS, estimator="MLM")

sem_fitmeasures(Fit_Fle_G)
```

### Measurement invariance across Gender
```{r MI flexibility gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Fle, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI flexibility institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Fle, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r reliability Flexibility, echo = F}
Fle_items_G <- dplyr::select(Goleweb_KYSS, K_Flex01, K_Flex02, K_Flex03,  K_Flex04,  K_Flex05, K_Flex06)
rel_Fle <- psych::alpha(Fle_items_G)

colformat_double(flextable(rel_Fle$total), digits = 2)
```


## Customer orientation

### CFA
```{r CFA Customer orientation, echo=F}
Model_Kla<-'
Klantgerichtheid=~K_Klant01+
K_Klant02+
K_Klant03+
K_Klant04+
K_Klant05+
K_Klant06
'

Fit_Kla_G <- cfa(model = Model_Kla, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Kla_G)
```

### Measurement invariance across Gender
```{r MI customer gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Kla, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI customer institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Kla, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r reliability customer, echo = F}
Klant_items_G <- dplyr::select(Goleweb_KYSS, K_Klant01, K_Klant02, K_Klant03, K_Klant04, K_Klant05, K_Klant06)
Rel_Klant <- psych::alpha(Klant_items_G)

colformat_double(flextable(Rel_Klant$total), digits = 2)
```


## Analysing

### CFA
```{r CFA Analysing, echo=F}
Model_Ana<-'
Analyseren=~K_Anal01+
K_Anal02+
K_Anal03+
K_Anal04+
K_Anal05
'

Fit_Ana_G <- cfa(model = Model_Ana, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Ana_G)
```

### Measurement invariance across Gender
```{r MI analysing gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Ana, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI analysing institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Ana, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r reliability analysing, echo = F}
Anal_items_G <- dplyr::select(Goleweb_KYSS, K_Anal01, K_Anal02, K_Anal03, K_Anal04, K_Anal05)
Rel_Anal <- psych::alpha(Anal_items_G)

colformat_double(flextable(Rel_Anal$total), digits = 2)
```


## Creativity

### CFA

```{r CFA Creativity, echo=F}
Model_Cre<-'
Creativiteit=~K_Crea01+
K_Crea02+
K_Crea03+
K_Crea04+
K_Crea05+
K_Crea06'

Fit_Cre_G <- cfa(model = Model_Cre, data = Goleweb_KYSS, estimator="MLM")
# summary(Fit_Cre_G, fit.measures = TRUE, standardized=TRUE) 

sem_fitmeasures(Fit_Cre_G)

```

### Measurement invariance across Gender
```{r MI creativity gender, echo = F, warning = FALSE}
MI_creativiteit<-measurementInvariance(model = Model_Cre, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI creativity institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Cre, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability

```{r reliability creativity, echo = F}
Cre_items_G <- dplyr::select(Goleweb_KYSS, K_Crea01,K_Crea02, K_Crea03, K_Crea04, K_Crea05, K_Crea06)
rel_Cre <- psych::alpha(Cre_items_G)

colformat_double(flextable(rel_Cre$total), digits = 2)
  
```


## Critical Thinking

### CFA
```{r CFA Critical Thinking, echo=F}
Model_Kri<-'
Kritischdenken=~K_Kriti01+
K_Kriti02+
K_Kriti03+
K_Kriti04+
K_Kriti05
'
Fit_Kri_G <- cfa(model = Model_Kri, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Kri_G)
```

### Measurement invariance across Gender
```{r MI critical gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Kri, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI critical institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Kri, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r reliability critical, echo = F}
Kriti_items_G <- dplyr::select(Goleweb_KYSS, K_Kriti01, K_Kriti02, K_Kriti03, K_Kriti04, K_Kriti05)
Rel_Kriti <- psych::alpha(Kriti_items_G)

colformat_double(flextable(Rel_Kriti$total), digits = 2)
```


## Willingness to learn

### CFA
```{r CFA Willingness to learn, echo=F}
Model_Leer<-'
Leerbereidheid=~K_Leer01+
K_Leer02+
K_Leer03+
K_Leer04+
K_Leer05+
K_Leer06
'
Fit_Leer_G <- cfa(model = Model_Leer, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Leer_G)
```

### Measurement invariance across Gender
```{r MI Learning gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Leer, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI Learning institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Leer, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r reliability learning}
Leer_items_G <- dplyr::select(Goleweb_KYSS, K_Leer01, K_Leer02, K_Leer03, K_Leer04, K_Leer05, K_Leer06)
Rel_Leer <- psych::alpha(Leer_items_G)

colformat_double(flextable(Rel_Leer$total), digits = 2)
```


## Self-reflection

### CFA
```{r CFA Self-reflection, echo=F}
    Model_Ref_G<-'
Zelfreflectie=~K_Refl01+
K_Refl02+
K_Refl03+
K_Refl04+
K_Refl05+
K_Relf06'

Fit_Ref_G <- cfa(model = Model_Ref_G, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Ref_G)
```
Fit measures demonstrate inadequate model fit. Modification indices pointed out that allowing covariance between items K_Refl03 and K_Refl04 would improve model fit.

```{r CFA reflection 2, echo=F}
Model_Ref_G2<-'
Zelfreflectie=~K_Refl01+
K_Refl02+
K_Refl03+
K_Refl04+
K_Refl05+
K_Relf06
K_Refl03~~K_Refl04'

Fit_Ref_G2 <- cfa(model = Model_Ref_G2, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Ref_G2)

```
Fit measures demonstrate that allowing covariance resulted in adequate model-fit. Analyses also pointed that the second model is significantly better than the first.

```{r CFA Reflection 3, echo=F}

compare_Ref <- anova (Fit_Ref_G, Fit_Ref_G2)

flextable(compare_Ref)

```

### Measurement invariance across Gender
```{r MI Reflection gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Ref_G2, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI Reflection institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Ref_G2, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r Reflection, echo = F}
Ref_items_G <- dplyr::select(Goleweb_KYSS, K_Refl01, K_Refl02, K_Refl03, K_Refl04, K_Refl05, K_Relf06)
Rel_Ref <- psych::alpha(Ref_items_G)

colformat_double(flextable(Rel_Ref$total), digits = 2)
```


## Planning & Organising

### CFA
```{r CFA Planning & organising, echo=F}
Model_Pla<-'
Plannen=~K_Plan01+
K_Plan02+
K_Plan03+
K_Plan04+
K_Plan05+
K_Plan06+
K_Plan07
'

Fit_Pla_G <- cfa(model = Model_Pla, data = Goleweb_KYSS, estimator="MLM")

sem_fitmeasures(Fit_Pla_G)
```

### Measurement invariance across Gender
```{r MI planning gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Pla, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI planning institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Pla, data = Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r reliability Planning, echo = F}

Pla_items_G <- dplyr::select(Goleweb_KYSS, K_Plan01, K_Plan02, K_Plan03, K_Plan04, K_Plan05, K_Plan06, K_Plan07)
Rel_Pla <- psych::alpha(Pla_items_G)

colformat_double(flextable(Rel_Pla$total), digits = 2)

```


## Responsibility

### CFA
```{r CFA Responsibility, echo=F}
Model_Ver<-'
Verantwoordelijkheid=~K_Vera01+
K_Vera02+
K_Vera03+
K_Vera04
'

Fit_Ver_G <- cfa(model = Model_Ver, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Ver_G)
```

### Measurement invariance across Gender
```{r MI responsibility gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Ver, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI responsibility institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Ver, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r reliability responsibility, echo = F}
Vera_items_G <- dplyr::select(Goleweb_KYSS, K_Vera01, K_Vera02, K_Vera03, K_Vera04)
Rel_Vera <- psych::alpha(Vera_items_G)

colformat_double(flextable(Rel_Vera$total), digits = 2)
```


## Independence

### CFA
```{r CFA Self-reliance, echo=F}
Model_Zelf<-'
Zelfstandigheid=~K_Zelf01+
K_Zelf02+
K_Zelf03+
K_Zelf04+
K_Zelf05+
K_Zelf06
'

Fit_Zelf_G <- cfa(model = Model_Zelf, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Zelf_G)
```

Fit measures demonstrate inadequate model fit. Modification indices pointed out that allowing covariance between items K_Zelf02 and K_Zelf04 would improve model fit.

```{r CFA Self-reliance 2, echo=F}
Model_Zelf_2<-'
Zelfstandigheid=~K_Zelf01+
K_Zelf02+
K_Zelf03+
K_Zelf04+
K_Zelf05+
K_Zelf06
K_Zelf02~~K_Zelf04'
 Fit_Zelf_G2 <- cfa(model = Model_Zelf_2, data = Goleweb_KYSS, estimator="MLM")
sem_fitmeasures(Fit_Zelf_G2)

```

### Measurement invariance across Gender
```{r MI reliance gender, echo = F, warning = FALSE}
measurementInvariance(model = Model_Zelf_2, data=Goleweb_KYSS, group="Gender", estimator="MLM")

```

### Measurement invariance across Institutions
```{r MI reliance institutions, echo = F, warning = FALSE}
measurementInvariance(model = Model_Zelf_2, data=Goleweb_KYSS, group="Institution", estimator="MLM")

```

### Reliability
```{r reliability self-reliance, echo = F}
Zelf_items_G <- dplyr::select(Goleweb_KYSS, K_Zelf01, K_Zelf02, K_Zelf03, K_Zelf04, K_Zelf05, K_Zelf06)
Rel_Zelf <- psych::alpha(Zelf_items_G)

colformat_double(flextable(Rel_Zelf$total), digits = 2)
```


## Conclusions Psychometric Analyses
